MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-14 docs/paper/out/paper.tex
reword first part of intro -- paper

Metagenomics data analysis is growing at exponential rate during the
last years. The increasing throughput of massively parallel sequencing
technologies, the derived decreasing cost, and the high impact of
metagenomics studies, especially in human health (diagnostics,
treatments, drug response, prevention), are crucial reasons responsible
for this growth of Metagenomics. There is a growing interest in
sequencing all kind of microbiomes (gut, mouth, skin, urinary tract,
airway, milk, bladder), in different conditions of health and disease,
or after different treatments. Metagenomics is also impacting
environmental sciences, crop sciences, agrifood sector and biotechnology
in general. This new possibilities for exploring the diversity of
micro-organisms in the most diverse environments is opening many new
research areas but, due to this wide interest, it is expected that the
amount of data will be overwhelming in the short time
\citep{stephens2015big}.

>>>>

During the past few years, metagenomics data analysis is growing
exponentially. Some of the reasons behind this are the increasing
throughput of massively parallel sequencing technologies (with the
derived decrease in sequencing costs), and the wide impact of
metagenomics studies, especially in human health (diagnostics,
treatments, drug response or prevention). We should also mention what
could be called the microbiome explosion: all kind of microbiomes (gut,
mouth, skin, urinary tract, airway, milk, bladder) are now routinely
sequenced in different conditions of health and disease, or after
different treatments. The impact of Metagenomics is also being felt in
environmental sciences, crop sciences, the agrifood sector and
biotechnology in general. These new possibilities for exploring the
diversity of micro--organisms in the most varied environments are
opening new research areas, and drastically changing the existing ones.

As a consequence, the challenge is thus moving (as in other fields) from
data acquisition to data analysis: the amount of data is expected to be
overwhelming in a very short time \citep{stephens2015big}.
